Enforced Invariant Confluence

### 2018-04-26 doc/paper/sections/evaluation.tex
Added TPC checks to paper.

\example[TPC-C]\examplelabel{TpccEval}
TPC-C is a ubiquitous OLTP database benchmark with a workload that models a
simple warehousing application~\cite{difallah2013oltp}. The TPC-C specification
outlines twelve ``consistency requirements'' (read invariants) that govern the
warehousing application. In~\cite{bailis2014coordination}, Bailis et al.\
categorize the invariants into one of three types:
\begin{enumerate}
  \item
    Three of the twelve invariants are \textbf{foreign key constraints}.  As
    discussed in \exampleref{ForeignKeysEval}, our decision procedures can
    automatically verify conditions under which foreign key constraints are
    \invariantconfluent{}.

  \item
    \newcommand{\ttt}[1]{{\smaller \texttt{#1}}} Seven of the twelve invariants
    involve \textbf{maintaining arithmetic relationships between relations}.
    Our decision procedures can correctly identify these as
    \invariantconfluent{}. Consider, for example, invariant 1 which dictates
    that a warehouse's year to date balance \ttt{W\_YTD} is equal to the sum of
    the district year to date balances \ttt{D\_YTD} of the twenty districts
    that are associated with the warehouse. The Payment transaction randomly
    selects a district and increments \ttt{W\_YTD} and \ttt{D\_YTD} by a
    randomly generated amount. We model this workload with a PN-Counter for
    \ttt{W\_YTD} and twenty PN-Counters for the twenty instances of
    \ttt{D\_YTD}. We applied Lucy to this workload, and it determined that the
    workload was \invariantconfluent{} in less than a second.

  \item
    Two of the twelve invariants involve generating \textbf{sequential and
    unique identifiers}. This workload is \emph{not} \invariantconfluent{}, but
    when the sequentiality requirement is dropped, it is \invariantconfluent{}.
    Unfortunately, modelling unique key generation in our theoretical framework
    (and in our prototype implementation) is not possible because we have thus
    far tacitly assumed that transaction execution is deterministic. We leave a
    generalization of our theory to non-deterministic transactions for future
    work.
\end{enumerate}

>>>>

\example[TPC-C]\examplelabel{TpccEval}
TPC-C is a ubiquitous OLTP database benchmark with a workload that models a
simple warehousing application~\cite{difallah2013oltp}. The TPC-C specification
outlines twelve ``consistency requirements'' (read invariants) that govern the
warehousing application. In~\cite{bailis2014coordination}, Bailis et al.\
categorize the invariants into one of three types:

% \begin{enumerate}
%   \item
    Three of the twelve invariants are \textbf{foreign key constraints}.  As
    discussed in \exampleref{ForeignKeysEval}, our decision procedures can
    automatically verify conditions under which foreign key constraints are
    \invariantconfluent{}.

  % \item
    \newcommand{\ttt}[1]{{\smaller \texttt{#1}}} Seven of the twelve invariants
    involve \textbf{maintaining arithmetic relationships between relations}.
    Our decision procedures can correctly identify these as
    \invariantconfluent{}. Consider, for example, invariant 1 which dictates
    that a warehouse's year to date balance \ttt{W\_YTD} is equal to the sum of
    the district year to date balances \ttt{D\_YTD} of the twenty districts
    that are associated with the warehouse. The Payment transaction randomly
    selects a district and increments \ttt{W\_YTD} and \ttt{D\_YTD} by a
    randomly generated amount. We model this workload with a PN-Counter for
    \ttt{W\_YTD} and twenty PN-Counters for the twenty instances of
    \ttt{D\_YTD}. We applied Lucy to this workload, and it determined that the
    workload was \invariantconfluent{} in less than a second.

  % \item
    Two of the twelve invariants involve generating \textbf{sequential and
    unique identifiers}. Consider, for example, invariant 2 which dictates that
    a district's next order id \ttt{D\_NEXT\_O\_ID} is equal to the maximum
    order id \ttt{O\_ID} of orders within the district. The New Order
    transaction places an order with \ttt{O\_ID} equal to the current value of
    \ttt{D\_NEXT\_O\_ID} and then increments \ttt{D\_NEXT\_O\_ID}. We model
    this workload with three objects. \ttt{D\_NEXT\_O\_ID} is modeled as an
    integer merged by $\max$. The order table is modelled as two objects. The
    first is a set of all order ids used, merged by union. The second is a map
    which maps order id to order. The map's merge function performs an id-by-id
    merge of orders. If two different orders have the same id, the merge
    function replaces them with a distinguished value to indicate that the
    primary key constraint has been violated. We applied Lucy to this workload
    and in less than a second, it produced a counterexample that---when
    labelled as reachable---proved that the workload was not
    \invariantconfluent{}.
% \end{enumerate}
